---
title: "fars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
```

# fars
Fars is simple package from coursera course "Mastering Software Development in R".
Its main goal is to simplify US accident data analysis, I, Ibrahim, will walk through the function to show what it can do


```{r eval=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(maps)
library(graphics)
```

The accident data has specific filenames, instead of using console or copying those manually, we can use `make_filename` to give us the correct username based on the year
```{r eval=FALSE}
fname <- make_filename(2015)
```
After that, we can use `fars_read` to load the data into tibble data frame.
```{r eval=FALSE}
df <- fars_read(fname)
head(df)
```
Now you're done! If you want to do your own analysis for one specific year, this is the end and now you can do what you want to do.

But this package has more than that! We can grab data from several years, add year column to it. This let you analyze several years data at once
```{r eval=FALSE}
df <- fars_read_years(c(2013, 2014))
head(df)
```
Now, if you want get a glance of the data based on year before dive down, we have simplify the process and give you summarised version of it.

```{r eval=FALSE}
df <- fars_summarize_years(c(2013, 2014, 2015))
head(df)
```
Last but not least, we have function to plot the accident into US map. You need to use correct state number for it to work (note: I don't know US state number since I'm not from US, so excuse my bad example)
```{r eval=FALSE}
fars_map_state(1,  2015)
```
